Benchmarking Principal Component Analysis software

### 2017-07-30 benchmark-pca.Rmd
benchmark pca OK

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.align = "center", out.width = "70%", 
                      fig.width = 16, fig.asp = 0.7, error = TRUE)
options(width = 80)
```

@@

```{r}
true <- fastpca("backingfiles/celiacQC_keep1", fast = FALSE)
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.align = "center", out.width = "70%", 
                      fig.width = 16, fig.asp = 0.7, error = TRUE)
options(width = 85)
```

@@

```{r}
# SmartPCA
smartpca <- fastpca("backingfiles/celiacQC_keep1", fast = FALSE)
true <- smartpca[[2]]
cat(sprintf("Standard PCA takes forever: %.2gh.", smartpca[[1]] / 3600))
```

@@

```{r, include=FALSE}
library(gmailr)
send_message(
  mime(To = "florian.prive.21@gmail.com",
       From = "florian.prive.21@gmail.com",
       Subject = sprintf("Knitting of %s has finished",
                         knitr::current_input()))
)
```
